### 2021-08-02 publications/2020-03-paper/revisions/review-responses.tex

% use the tnoteref command within \title for footnotes;
% use the tnotetext command for the associated footnote;
% use the fnref command within \author or \address for footnotes;
% use the fntext command for the associated footnote;
% use the corref command within \author for corresponding author footnotes;
% use the cortext command for the associated footnote;
% use the ead command for the email address,
% and the form \ead[url] for the home page:
%
% \title{Title\tnoteref{label1}}
% \tnotetext[label1]{}
% \author{Name\corref{cor1}\fnref{label2}}
% \ead{email address}
% \ead[url]{home page}
% \fntext[label2]{}
% \cortext[cor1]{}
% \address{Address\fnref{label3}}
% \fntext[label3]{}

\title{The role of current and emerging technologies in meeting Japan's mid- to long-term carbon reduction goals\\
\large Response to Editor and Review Comments}
\author{Anshuman Chaube, Andrew Chapman, Akari Minami, James Stubbins, Kathryn Huff}

% use optional labels to link authors explicitly to addresses:
% \author[label1,label2]{<author name>}
% \address[label1]{<address>}
% \address[label2]{<address>}

%\author[uiuc]{Kathryn Huff}
%        \ead{kdhuff@illinois.edu}
%  \address[uiuc]{Department of Nuclear, Plasma, and Radiological Engineering,
%        118 Talbot Laboratory, MC 234, Universicy of Illinois at
%        Urbana-Champaign, Urbana, IL 61801}
%
% \end{frontmatter}
\maketitle
\section*{Review General Response}
We would like to thank the reviewers and editors for their detailed assessment of
this paper. Your suggestions, clarifications, and comments have resulted in 
changes which improved the paper. This version adds detailed responses to the Editor's comments. Changes made are reflected in both the revised copy \texttt{times-paper-revised.pdf} and the ``track-changes" copy \texttt{times-paper-changes.pdf}.

\begin{questions}

        \section*{Editor's Comments}

         \question REVISION FORMAT: Please include both ``TRACK CHANGES" revision (not only marked in coloured highlighting but also with tracked changes to indicate the original and revised versions) as well as a clean version.

        \begin{solution}
                Thank you for these comments. This ``track changes" revision has been provided in \texttt{times-paper-changes.pdf}, in which the changes are highlighted in blue. Not only have the changes been highlighted, but the removed text has been denoted with a strikethrough line and the added text is in plain blue. This matches the requirement of indicating the changes in the original and revised versions by tracking changes beyond coloured highlighting. Please note that we used Latex's track changes feature as Applied Energy does not prescribe the use of any particular word processor or text editor, only that the changes be tracked and highlighted. Any other format is not possible as we have used Latex to prepare our paper.

         \question RELEVANCE: The relevance to energy related issues should be enhanced. Please note Applied Energy is focused on energy related topics with emphasis on application.

        \begin{solution}
                Thank you for these comments. The focus of the paper is entirely on applied energy-related issues, in that we use an energy analysis code to simulate a variety of realistic near- to long-term transition scenarios for a developed nation. Our analysis is grounded in the realities of the existing energy landscape and carbon emission goals, and takes into account a wide variety of emerging energy technologies.

     \question  PROOF READING: Proof reading by a native English speaker should be conducted to improve both language and organization quality.

        \begin{solution}
                Thank you for these comments. Our co-authors Chapman, Stubbins, and Huff are native speakers of English who have proof-read the paper and approved the quality of the language and organisation within the paper.

 \question ORGANIZATION: In addition to detailed discussions and analyses of the results, the whole paper shall be written as an integrated article with the new results responding to the research questions (objectives). Detailed descriptions such as equations, input data/datasets and assumptions, or system components can be briefly discussed in the main text and leave the detailed materials in the APPENDIX.

        \begin{solution}
                Thank you for these comments. Our paper closely follows this structure, with the main results integrated into a cohesive narrative, and with an appendix that has secondary details necessary to fully understand and reproduce our analysis.

\question  
ABBREVIATIONS: Please avoid using abbreviations in the TITLE, HIGHLIGHTS, ABSTRACT, and CONCLUSION, if possible.

        \begin{solution}
                Thank you for these comments. We largely avoid acronyms in the sections mentioned. A few acronyms related to the energy analysis software used (TIMES) and key transition technologies are mentioned as keywords to attract our target audience and to convey salient features of our methodology and results in a concise way. Their use will improve the readability of our paper and its ease of discovery by energy analysis experts reviewing literature similar to our work.

   \question  
REFERENCES AND CITING: Please also avoid "lump sum references", such as XXXXX [1-5], OR 1, 2, 3, 4, 5; all references should be cited with detailed and specific descriptions.  In the references, all authors (if less than 6 authors) should be included; avoid using "et al.” For more than 6 authors, the first 6 should be listed, followed by "et al."        
        \begin{solution}
                Thank you for these comments. We largely avoid lump sum references, except where multiple references are necessary to obtain a particular simulation parameter, or to demonstrate to the reader that a consensus exists around key simulation parameters or assumptions used. The following ``lump sum" references have been split based on your recommendation:
                \begin{itemize}

\item On page 2, line 11 - references [4,5] have been split into [4] and [5].

\item On page 2, last line - references [7,10,11] have been split into [10,11] and [7].

    %------------------------------------

   \question

TITLE: The title normally consists of about 12-15 keywords, which shall not be too general or too narrow.        
        \begin{solution}
                Thank you for these comments. Our title is 17 keywords, which is in agreement with "about 12-15". It includes two that are part of a hyphenated term (mid- and long-term). We consider the title adequate and necessary to succinctly convey the objective as well as the novelty of our work.

    %------------------------------------

 \question

HIGHLIGHTS: Highlights are mandatory for this journal. They consist of a short collection of bullet points that convey the core NEW findings of the article, and should be submitted in a separate editable file in the online submission system. Please use 'Highlights' in the file name, and include 3 to 5 bullet points (maximum 85 characters, including spaces, per bullet point).

 \begin{solution}
                Thank you for these comments. We have submitted highlights in the prescribed format.

    %------------------------------------

 \question

ABSTRACT: The abstract should be about 150-250 words, with concise text in a single paragraph. Answer the questions: What problem did you study and why is it important? What methods did you use? What were your main results? And what conclusions can you draw from your results? Please include in your abstract more specific and quantitative results when it suits broader audiences. The abstract stands alone: no references, figures, tables or equations are cited.

 \begin{solution}
                Thank you for these comments. Our abstract adheres to the format described above and addresses each question mentioned above.

    %------------------------------------

 \question

CAPTIONS: Captions for figures and tables should be presented with more specific descriptions rather than general sentences like "Results of the experiments ...", "A studied system ...."

 \begin{solution}
                Thank you for these comments. Our captions are in accordance with the above guidelines.

    %------------------------------------       
      \question

UNITS: SI units shall be used.

 \begin{solution}
                Thank you for these comments. Our paper largely uses SI units. The sole exception to this is the values of life-cycle emissions or emission coefficients, which are in $g-CO_2/kWh$. This is in accordance with the conventions used in lifecycle analysis by other authors and organisations (e.g.: the IPCC) in the field, and it is also necessary to avoid long suffixes such as $\times 10^{-3}$ or $\times 10^{-6}$ that are associated with the small emission coefficient values of existing and emerging low-carbon technologies.

    %------------------------------------

  \question

DATA: All data shall be carefully presented with consistent accuracy. Uncertainty of input data/assumptions shall be addressed.

 \begin{solution}
                Thank you for these comments. Our paper presents all simulation parameters used in as much detail as possible within the methodology section and the appendix, in addition to providing a link to our simulation input files as a reference. Assumptions and uncertainty regarding the input parameters of emerging technologies has been discussed in the methodologies section. The references cited for each technology's data provide further details on the calculation and uncertainty of each parameter. The overall uncertainty associated with these transitions has been dealt with by simulating multiple transition scenarios with different likely combinations of emerging technologies, and by conducting a sensitivity analysis based on likely ranges of input parameters.

    %------------------------------------        
      \question

CONCLUSION: The paragraph shall be independent from the main text, without citing tables, figures or references. It should be concise, including the most important new findings.

 \begin{solution}
                Thank you for these comments. Our conclusion adheres to these guidelines for the most part, however the first paragraph of conclusions has been modified to remove references to specific figures.

    %------------------------------------        
        \question

ORIGINALITY: The originality of the paper needs to be further clarified. Sufficient results are important to justify the novelty of a high-quality journal paper.

 \begin{solution}
                Thank you for these comments. We have highlighted the novelty of the paper across the abstract, highlights, and the last paragraphs of both the introduction and the literature review by pointing to the wide range of emerging technologies considered, the dynamic incorporation of learning curves for economic parameters and lifecycle emissions, the use of five different transition scenarios, the assessment of their long-term impact on the energy system and emissions, and the use of sensitivity analysis to identify key technologies, parameters, and trade-offs. The following sentence has been added to the end of the Literature Review section to further emphasize the novelty of our paper:
                \begin{itemize}

\item "Our sensitivity analysis is another novel aspect of our research, in that it elicits important technologies and their key parameters while remaining grounded in the context of the carbon constraints and the initial conditions that are reflective of many developed nations that aim to reduce their emissions."

    %------------------------------------        
              \question

LITERATURE REVIEW:  An updated and complete literature review should be conducted to present the state-of-the-art and knowledge gaps in the research, with strong relevance to the topic of the paper.
 \begin{solution}
                Thank you for these comments. Our literature review follows these guidelines by highlighting the previous research done in this field, the emerging consensus from literature, and how our research builds upon this body of work by extending transition scenario simulation by incorporating dynamic simulation parameters, a wide-variety of emerging technologies, and using sensitivity analysis to derive key insights that are not present in the literature reviewed.

    %------------------------------------   
          \question

APPLIED VALUES: The results should be further elaborated to show how they could be used for real applications. Modeling results should be validated by experiments.
 \begin{solution}
                Thank you for these comments. Our results are focused on a real energy system and the exploration of realistic transition pathways that reduce carbon emissions using existing or pre-commercialisation stage technology solutions. Validation is impossible as the changes to a nation's energy system cannot by simulated by experiments, long-term impacts cannot be re-created within our lifetimes, and emerging technologies cannot be accessed before maturity.

    %------------------------------------

       \question

INTERNATIONAL PERSPECTIVE: The paper shall not be discussed from the viewpoint of only one country.
 \begin{solution}
                Thank you for these comments. Our abstract and introduction highlight that the paper uses Japan as a proxy for any developed nation planning on undertaking a similar decarbonisation-focussed energy transition. This requirement was also pointed out by Dr. Yan, the editor, before the reviewers were assigned. The paper was modified based on his feedback and accepted, before being forwarded to reviewers.

    %------------------------------------

        \section*{Reviewer 1}

### 2021-08-02 publications/2020-03-paper/changes/conclusion-revised.tex
addresses editor's comments

We simulated five transition scenarios which assess potential pathways to meeting 2030 and 2050 emission targets within the Japanese electricity supply system and their long-term impact up to 2100. Scenario 1 (Figure \ref{scen1}) proved that meeting emission goals without new nuclear or new low-emission technologies is infeasible, and such an endeavour is likely to be an expensive failure. The remaining scenarios demonstrate that emission goals can be met by either investing heavily in nuclear (Figure \ref{scen2}), investing heavily in hydrogen (Figs. \ref{scen3} and \ref{scen5}), or using a combination of both (Figure \ref{scen4}). Scenarios that incorporate nuclear are the most cost-effective, and using a combination of nuclear and hydrogen leads to the greatest emission reduction post-2050. Key technologies that emerge from are results include nuclear power and hydrogen from renewables, while \gls{CCS} with natural gas and photochemical water splitting (\gls{PWS}) play a nominal role. CCS with coal, steam reforming with or without CCS, new coal, and new oil are not utilised due to their high direct and life-cycle emissions. Our analysis indicates that while politically challenging, a hybrid nuclear-hydrogen strategy is economically feasible and results in long-term emission reduction. Such a multifaceted approach to emission reduction is also likely to improve decarbonisation outcomes since the commercialisation and deployment of hydrogen in time to meet 2030 and 2050 emission goals is uncertain.

>>>>

We simulated five transition scenarios which assess potential pathways to meeting 2030 and 2050 emission targets within the Japanese electricity supply system and their long-term impact up to 2100. \deleted{Scenario 1 (Figure \ref{scen1})} \added{Our transition scenarios} prove\deleted{d} that meeting emission goals without new nuclear or new low-emission technologies is infeasible, and such an endeavour is likely to be an expensive failure. \deleted{The remaining scenarios} \added{These results also} demonstrate that emission goals can be met by either investing heavily in nuclear \deleted{(Figure \ref{scen2})}, investing heavily in hydrogen \deleted{(Figs. \ref{scen3} and \ref{scen5})}, or using a combination of both \deleted{(Figure \ref{scen4})}. Scenarios that incorporate nuclear are the most cost-effective, and using a combination of nuclear and hydrogen leads to the greatest emission reduction post-2050. Key technologies that emerge from are results include nuclear power and hydrogen from renewables, while \gls{CCS} with natural gas and photochemical water splitting (\gls{PWS}) play a nominal role. CCS with coal, steam reforming with or without CCS, new coal, and new oil are not utilised due to their high direct and life-cycle emissions. Our analysis indicates that while politically challenging, a hybrid nuclear-hydrogen strategy is economically feasible and results in long-term emission reduction. Such a multifaceted approach to emission reduction is also likely to improve decarbonisation outcomes since the commercialisation and deployment of hydrogen in time to meet 2030 and 2050 emission goals is uncertain.

### 2021-08-02 publications/2020-03-paper/revisions/conclusion.tex
minor changes to reviewer comments
addresses editor's comments

We simulated five transition scenarios which assess potential pathways to meeting 2030 and 2050 emission targets within the Japanese electricity supply system and their long-term impact up to 2100. Scenario 1 (Figure \ref{scen1}) proved that meeting emission goals without new nuclear or new low-emission technologies is infeasible, and such an endeavour is likely to be an expensive failure. The remaining scenarios demonstrate that emission goals can be met by either investing heavily in nuclear (Figure \ref{scen2}), investing heavily in hydrogen (Figs. \ref{scen3} and \ref{scen5}), or using a combination of both (Figure \ref{scen4}). Scenarios that incorporate nuclear are the most cost-effective, and using a combination of nuclear and hydrogen leads to the greatest emission reduction post-2050. Key technologies that emerge from are results include nuclear power and hydrogen from renewables, while \gls{CCS} with natural gas and photochemical water splitting (\gls{PWS}) play a nominal role. CCS with coal, steam reforming with or without CCS, new coal, and new oil are not utilised due to their high direct and life-cycle emissions. Our analysis indicates that while politically challenging, a hybrid nuclear-hydrogen strategy is economically feasible and results in long-term emission reduction. Such a multifaceted approach to emission reduction is also likely to improve decarbonisation outcomes since the commercialisation and deployment of hydrogen in time to meet 2030 and 2050 emission goals is uncertain.

Mitigating emissions from the industrial and transportation sector presents unique challenges that may affect the amount of emission reduction required from the electricity supply sector to meet Japan's 2030 and 2050 goals. Future work should incorporate holistic assessment of the entire Japanese energy system when exploring energy transition pathways. The assessment of synergistic utilisation of hydrogen in transportation and industry alongside electricity storage and supply is vital for policy decisions. The effect of transportation media such as trucks and pipelines on hydrogen and CCS is also worth investigating. Finally, economic feasibility analyses with respect to national budget requirements and projected GDP trends must also be conducted to improve decarbonisation strategies, improve social outcomes, and delineate investment goals for the energy sector.

>>>>

We simulated five transition scenarios which assess potential pathways to meeting 2030 and 2050 emission targets within the Japanese electricity supply system and their long-term impact up to 2100. Our transition scenarios prove that meeting emission goals without new nuclear or new low-emission technologies is infeasible, and such an endeavour is likely to be an expensive failure. These results also demonstrate that emission goals can be met by either investing heavily in nuclear, investing heavily in hydrogen, or using a combination of both. Scenarios that incorporate nuclear are the most cost-effective, and using a combination of nuclear and hydrogen leads to the greatest emission reduction post-2050. Key technologies that emerge from are results include nuclear power and hydrogen from renewables, while \gls{CCS} with natural gas and photochemical water splitting (\gls{PWS}) play a nominal role. CCS with coal, steam reforming with or without CCS, new coal, and new oil are not utilised due to their high direct and life-cycle emissions. Our analysis indicates that while politically challenging, a hybrid nuclear-hydrogen strategy is economically feasible and results in long-term emission reduction. Such a multifaceted approach to emission reduction is also likely to improve decarbonisation outcomes since the commercialisation and deployment of hydrogen in time to meet 2030 and 2050 emission goals is uncertain.

Mitigating emissions from the industrial and transportation sector presents unique challenges that may affect the amount of emission reduction required from the electricity supply sector to meet Japan's 2030 and 2050 goals. Future work should incorporate holistic assessment of the entire Japanese energy system when exploring energy transition pathways. The assessment of synergistic utilisation of hydrogen in transportation and industry alongside electricity storage and supply is vital for policy decisions. The effect of transportation media such as trucks and pipelines on hydrogen and CCS is also worth investigating. Any new technologies that develop in the future and promise rapid decarbonisation should also be incorporated in such work. Finally, economic feasibility analyses with respect to national budget requirements and projected GDP trends must also be conducted to improve decarbonisation strategies, improve social outcomes, and delineate investment goals for the energy sector.

### 2021-08-02 publications/2020-03-paper/revisions/cover-letter-2/cover_letter.tex
addresses editor's comments

Thank you for giving us the opportunity to revise and resubmit our manuscript. The comments provided by the reviewers were considered seriously and their feedback has improved the readability and academic rigour of our work.

We look forward to working with you towards moving towards publication.

>>>>

Thank you for giving us the opportunity to address editors' comments. We are pleased that the reviewers have approved the revision of our manuscript. We look forward to working with you on moving towards publication.

### 2021-08-02 publications/2020-03-paper/revisions/introduction.tex
addresses editor's comments

We are probing these questions by simulating cost-optimised energy transitions in the electricity supply sector with rigid carbon constraints using a suite of existing and emerging electricity generation and storage technologies. We use Japan as a proxy for a developed nation committed to addressing climate change. However, the results have global significance. Like many other developed nations, Japan has been rapidly deploying renewables, and in the wake of the Fukushima Daiichi accident, it shut down its nuclear reactors and increased its reliance on coal \cite{international_energy_agency_latest_2019, noauthor_electricity_2019}. However, now Japan is reinvigorating its nuclear power sector, as evidenced by the restart of some of its nuclear reactors \cite{iaea_pris_nodate}. Additionally, Japan is actively developing plans to deploy hydrogen power under the Basic Hydrogen Strategy \cite{noauthor_basic_2017} and has shown interest in utilising \gls{CCS} \cite{meti_report_2020}. Therefore, due to Japan's similarity to other developed nations and its willingness to consider a variety of commercial and pre-commercial low-carbon technologies, simulating likely transition pathways for decarbonisation of the Japanese electricity sector could inform global energy policy. Our simulations provide these insights by delineating potential transition scenarios that consider multiple combinations of a variety of technological options, and our sensitivity analyses identify key novel technologies and their most significant parameters.

@@

The context of the Japanese transition strategy also captures the priorities, subtle limitations, and lack of specificity in other developed nations' energy transition plans. Although influenced by the Paris Agreements, Japanese energy policy is governed chiefly by the Basic Energy Plan \cite{noauthor_basic_2017}, which outlines national policy towards a new energy system for the years 2030 and 2050 cognizant of limited indigenous resources, the impact of the Fukushima incident, and external pressures on energy supplies \cite{meti_annual_2018}. The plan reaffirms Japanese benchmarks for evaluating the energy system, first and foremost, within the context of energy security, followed by economic efficiency, safety, and the environment (summarised as `3E+S'; ibid). Although the Japanese 3E+S goals and the Paris Agreement targets have some parallels, the plan does not detail how the 2050 emission reduction target of 80\% is to be met. Matsuo et. al have suggested that electrification of a number of sectors will be required to achieve the ambitious 2050 target, underpinned by low-carbon technologies \cite{matsuo_quantitative_2018}. For the power sector to achieve such a target, near-zero emissions are required, and early action utilising existing technologies is preferable to delayed action utilising future technologies \cite{ashina_roadmap_2012}. The strategies currently under consideration include reinvigorating nuclear power, deploying \gls{CCS} to fossil fuel power plants, and ushering in a hydrogen economy based on renewable energy-based electrolysis as well as hydrogen imports from abroad \cite{ashina_roadmap_2012, matsuo_quantitative_2018, noauthor_basic_2017}.

>>>>

We are probing these questions by simulating cost-optimised energy transitions in the electricity supply sector with rigid carbon constraints using a suite of existing and emerging electricity generation and storage technologies. We use Japan as a proxy for a developed nation committed to addressing climate change. However, the results have global significance. Like many other developed nations, Japan has been rapidly deploying renewables, and in the wake of the Fukushima Daiichi accident, it shut down its nuclear reactors \cite{international_energy_agency_latest_2019} and increased its reliance on coal  \cite{noauthor_electricity_2019}. However, now Japan is reinvigorating its nuclear power sector, as evidenced by the restart of some of its nuclear reactors \cite{iaea_pris_nodate}. Additionally, Japan is actively developing plans to deploy hydrogen power under the Basic Hydrogen Strategy \cite{noauthor_basic_2017} and has shown interest in utilising \gls{CCS} \cite{meti_report_2020}. Therefore, due to Japan's similarity to other developed nations and its willingness to consider a variety of commercial and pre-commercial low-carbon technologies, simulating likely transition pathways for decarbonisation of the Japanese electricity sector could inform global energy policy. Our simulations provide these insights by delineating potential transition scenarios that consider multiple combinations of a variety of technological options, and our sensitivity analyses identify key novel technologies and their most significant parameters.

@@

The context of the Japanese transition strategy also captures the priorities, subtle limitations, and lack of specificity in other developed nations' energy transition plans. Although influenced by the Paris Agreements, Japanese energy policy is governed chiefly by the Basic Energy Plan \cite{noauthor_basic_2017}, which outlines national policy towards a new energy system for the years 2030 and 2050 cognizant of limited indigenous resources, the impact of the Fukushima incident, and external pressures on energy supplies \cite{meti_annual_2018}. The plan reaffirms Japanese benchmarks for evaluating the energy system, first and foremost, within the context of energy security, followed by economic efficiency, safety, and the environment (summarised as `3E+S'; ibid). Although the Japanese 3E+S goals and the Paris Agreement targets have some parallels, the plan does not detail how the 2050 emission reduction target of 80\% is to be met. Matsuo et. al have suggested that electrification of a number of sectors will be required to achieve the ambitious 2050 target, underpinned by low-carbon technologies \cite{matsuo_quantitative_2018}. For the power sector to achieve such a target, near-zero emissions are required, and early action utilising existing technologies is preferable to delayed action utilising future technologies \cite{ashina_roadmap_2012}. The strategies currently under consideration include reinvigorating nuclear power, deploying \gls{CCS} to fossil fuel power plants, and ushering in a hydrogen economy based on renewable energy-based electrolysis \cite{ashina_roadmap_2012, matsuo_quantitative_2018} as well as hydrogen imports from abroad \cite{noauthor_basic_2017}.

### 2021-08-02 publications/2020-03-paper/revisions/litreview.tex
adds response to reviewer 2
addresses editor's comments

\section{Background and literature review} \label{litreview}
The Paris Agreement commits individual nations to significant carbon reduction over time through the \gls{INDC} mechanism \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}. Japan, as a signatory to the Paris Agreements, has submitted an INDC with the following goals and timelines: reduce GHG emissions by 26\% compared to 2013 levels by 2030, and reduce overall GHG emissions by 80\% or more by 2050, through the ``development and diffusion of low-carbon technologies and transition to a low-carbon socio-economic structure" \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}. 
Aware of these targets, many researchers have evaluated Japan's future energy system using a variety of modelling approaches, which we review below. Using the \gls{MARKAL} model, considering the uncertainties of technology development, Ozawa et al. found that hydrogen will play a major role in the future energy system, reliant on both nuclear power and \gls{CCS} to reduce electricity sector emissions to nearly zero by 2050 \cite{ozawa_hydrogen_2018}. Recognising the benefits that renewable energy will play in reducing carbon emissions, and the issues of intermittency of renewables, Li et al. explored the role of hydrogen as a storage medium through power-to-gas approaches in Kyushu, Japan. Their study identified that power-to-gas can increase the effective utilisation rate of renewable energy, and the use of hydrogen in the gas network, effectively pairing the electricity and gas networks, overcomes current renewable electricity curtailment issues \cite{li_potential_2019}. Cognizant of the Japanese government's strategic approach to carbon reduction out to 2050 via energy system reform, Chapman and Pambudi also identify a strong role for nuclear, renewables, and hydrogen under a carbon constrained, optimal cost MARKAL/TIMES simulation approach \cite{chapman_strategic_2018}. Considering Japan's economic conditions and demographic trends, such as moderate GDP growth and rapid ageing, Kuriyama et al. suggest that 2030 targets can be met or exceeded (with up to 42\% GHG reduction) with limited renewable energy growth and a 15\% contribution from nuclear, or without nuclear, under a renewable growth scenario \cite{kuriyama_can_2019}. However, these trends and energy system changes will likely be insufficient to meet the more ambitious 2050 targets.

Taking a more holistic view in line with the Japanese government's 3E+S targets, ambitious research and development to enable high levels of renewable deployment is necessary to not only meet deep emission reduction goals, but to also reduce Japanese dependence on imported fuels, which would affect both CCS and nuclear deployment rates into the future. Consensus on policy options and priorities also has a large influence on modelling outcomes for the Low Carbon Navigator, which assesses Japanese energy and emission options out to 2050 \cite{moinuddin_japan_2019}. A seminal work by Sugiyama et al. harmonises a number of modelling approaches for Japan's long-term (up to 2050) climate change mitigation options, utilising national and global general and partial equilibrium models \cite{sugiyama_japans_2019}. Model results are contrasted under six scenarios which incorporate a baseline, a range of emissions reductions (50-80\%), and regional obligations for global models (ibid.) under the Paris Agreement target of an 80\% reduction. Each of the models assessed recognise the importance of renewable energy deployment by 2050, notably hydro, solar, and wind, with varying contributions from nuclear energy and fossil fuels, predominantly natural gas. Additionally, for Japan, the option of importing carbon-free hydrogen was identified as potentially playing a critical role \cite{akimoto_estimates_2010, matsuo_global_2013, oshiro_diffusion_2015, sugiyama_japans_2019}. Many studies consider hydrogen a critical part of Japan's low-carbon energy transition, as it can improve energy security, it can be produced from multiple sources, and lacks emissions from fuel combustion \cite{iida_hydrogen_2019}. Global modelling efforts consider the incorporation of long-distance international transport of hydrogen with end uses dominated by passenger and freight fuel cell vehicles and power generation, via both mixed and direct combustion. Electricity from hydrogen is estimated to emerge in Japan from 2030 onwards, as nuclear and coal-fired power generation reduce towards 2050 \cite{ishimoto_significance_2017}. From a policy standpoint, Japan has committed to achieving a hydrogen society, with the primary goal of cost parity of hydrogen with competing fuels, which requires a three-fold reduction in cost by 2030 and further reductions into the future \cite{nagashima_japans_2018}. Under the Basic Hydrogen Strategy, the Japanese government aims to realise low cost hydrogen use in power generation, mobility, and industry, develop international supply chains to ensure stable supply, expand renewable deployment, revitalise regional areas, and develop hydrogen related technologies \cite{meti_basic_2017}. The strategy aims to account for both economic and geopolitical impacts and the need to prioritise research and development to overcome the economic and technical challenges \cite{nagashima_japans_2018}. A common thread across previous research is the uncertainty surrounding \gls{CCS}, particularly with regard to scaling up and public acceptance issues, and the role that nuclear energy will play, largely due to policy reform which occurred after the Fukushima nuclear accident \cite{oshiro_mid-century_2019}.

The model and the approach proposed in this research uniquely build on the modelling consensus outlined in the literature review and expand the consideration of technologies by including emerging near-term alternatives, and potentially disruptive technologies post-2050. This work leverages the dynamic simulation capabilities of \gls{TIMES} \cite{loulou_etsap-tiam_2008} by incorporating learning curves for parameters such as investment and \gls{OM} costs, efficiency, and emission coefficients. Our model incorporates not only direct emissions, but also lifecycle emissions of all conventional and emerging technologies, the latter of which is an often neglected externality. This enables a more meaningful analysis of the global warming potential of emerging technologies, as life-cycle emissions become significant when considering deep emission reductions of the order of 80\% from current levels. By modelling the Japanese electricity supply system out to the year 2100, our aim is to detail the mid- to long-term impacts of technological development and market penetration, and to identify the suite of technologies which could underpin the successful achievement of carbon reduction.

>>>>

\section{Background and literature review} \label{litreview}
The Paris Agreement commits individual nations to significant carbon reduction over time through the \gls{INDC} mechanism \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}. Japan, as a signatory to the Paris Agreements, has submitted an INDC with the following goals and timelines: reduce GHG emissions by 26\% compared to 2013 levels by 2030, and reduce overall GHG emissions by 80\% or more by 2050, through the ``development and diffusion of low-carbon technologies and transition to a low-carbon socio-economic structure" \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}. 
Aware of these targets, many researchers have evaluated Japan's future energy system using a variety of modelling approaches, which we review below. Using the \gls{MARKAL} model, considering the uncertainties of technology development, Ozawa et al. found that hydrogen will play a major role in the future energy system, reliant on both nuclear power and \gls{CCS} to reduce electricity sector emissions to nearly zero by 2050 \cite{ozawa_hydrogen_2018}. Recognising the benefits that renewable energy will play in reducing carbon emissions, and the issues of intermittency of renewables, Li et al. explored the role of hydrogen as a storage medium through power-to-gas approaches in Kyushu, Japan. Their study identified that power-to-gas can increase the effective utilisation rate of renewable energy, and the use of hydrogen in the gas network, effectively pairing the electricity and gas networks, overcomes current renewable electricity curtailment issues \cite{li_potential_2019}. Cognizant of the Japanese government's strategic approach to carbon reduction out to 2050 via energy system reform, Chapman and Pambudi also identify a strong role for nuclear, renewables, and hydrogen under a carbon constrained, optimal cost MARKAL/TIMES simulation approach \cite{chapman_strategic_2018}. Considering Japan's economic conditions and demographic trends, such as moderate GDP growth and rapid population ageing, Kuriyama et al. suggest that 2030 targets can be met or exceeded (with up to 42\% GHG reduction) with limited renewable energy growth and a 15\% contribution from nuclear, or without nuclear, under a renewable growth scenario \cite{kuriyama_can_2019}. However, these trends and energy system changes will likely be insufficient to meet the more ambitious 2050 targets.

Taking a more holistic view in line with the Japanese government's 3E+S targets, ambitious research and development to enable high levels of renewable deployment is necessary to not only meet deep emission reduction goals, but to also reduce Japanese dependence on imported fuels, which would affect both CCS and nuclear deployment rates into the future. Consensus on policy options and priorities also has a large influence on modelling outcomes for the Low Carbon Navigator, which assesses Japanese energy and emission options out to 2050 \cite{moinuddin_japan_2019}. A seminal work by Sugiyama et al. harmonises a number of modelling approaches for Japan's long-term (up to 2050) climate change mitigation options, utilising national and global general and partial equilibrium models \cite{sugiyama_japans_2019}. Model results are contrasted under six scenarios which incorporate a baseline, a range of emissions reductions (50-80\%), and regional obligations for global models (ibid.) under the Paris Agreement target of an 80\% reduction. Each of the models assessed recognise the importance of renewable energy deployment by 2050, notably hydro, solar, and wind, with varying contributions from nuclear energy and fossil fuels, predominantly natural gas. Additionally, for Japan, the option of importing carbon-free hydrogen was identified as potentially playing a critical role \cite{akimoto_estimates_2010, matsuo_global_2013, oshiro_diffusion_2015, sugiyama_japans_2019}. Many studies consider hydrogen a critical part of Japan's low-carbon energy transition, as it can improve energy security, it can be produced from multiple sources, and lacks emissions from fuel combustion \cite{iida_hydrogen_2019}. Global modelling efforts consider the incorporation of long-distance international transport of hydrogen with end uses dominated by passenger and freight fuel cell vehicles and power generation, via both mixed and direct combustion. Electricity from hydrogen is estimated to emerge in Japan from 2030 onwards, as nuclear and coal-fired power generation reduce towards 2050 \cite{ishimoto_significance_2017}. From a policy standpoint, Japan has committed to achieving a hydrogen society, with the primary goal of cost parity of hydrogen with competing fuels, which requires a three-fold reduction in cost by 2030 and further reductions into the future \cite{nagashima_japans_2018}. Under the Basic Hydrogen Strategy, the Japanese government aims to realise low cost hydrogen use in power generation, mobility, and industry, develop international supply chains to ensure stable supply, expand renewable deployment, revitalise regional areas, and develop hydrogen related technologies \cite{noauthor_basic_2017}. The strategy aims to account for both economic and geopolitical impacts and the need to prioritise research and development to overcome the economic and technical challenges \cite{nagashima_japans_2018}. A common thread across previous research is the uncertainty surrounding \gls{CCS}, particularly with regard to scaling up and public acceptance issues, and the role that nuclear energy will play, largely due to policy reform which occurred after the Fukushima nuclear accident \cite{oshiro_mid-century_2019}.

The model and the approach proposed in this research uniquely build on the modelling consensus outlined in the literature review and expand the consideration of technologies by including emerging near-term alternatives, and potentially disruptive technologies post-2050. This work leverages the dynamic simulation capabilities of \gls{TIMES} \cite{loulou_etsap-tiam:_2008} by incorporating learning curves for parameters such as investment and \gls{OM} costs, efficiency, and emission coefficients. Our model incorporates not only direct emissions, but also lifecycle emissions of all conventional and emerging technologies, the latter of which is an often neglected externality. This enables a more meaningful analysis of the global warming potential of emerging technologies, as life-cycle emissions become significant when considering deep emission reductions of the order of 80\% from current levels. By modelling the Japanese electricity supply system out to the year 2100, our aim is to detail the mid- to long-term impacts of technological development and market penetration, and to identify the suite of technologies which could underpin the successful achievement of carbon reduction. Our sensitivity analysis is another novel aspect of our research, in that it elicits important technologies and their key parameters while remaining grounded in the context of the carbon constraints and the initial conditions that are reflective of many developed nations that aim to reduce their emissions.
